Supplementary Methods

### 2020-05-23 methods.tex
Move methods to standalone PDF

\section*{Methods}

@@

\subsection*{Library organization}

@@

\paragraph{\emph{Core.}}  The \code{ndarray} data structure and the
universal functions make up the core of NumPy.

@@

\paragraph{\emph{Computing libraries.}}
NumPy provides a large library of functions for array manipulation
and scientific computing, including functions for: creating, reshaping,
concatenating, and padding arrays; searching, sorting and counting data
in arrays; computing elementary statistics, such as the mean, median,
variance, and standard deviation; file I/O; and more.

@@

\paragraph{\emph{Infrastructure libraries.}} NumPy provides utilities
for writing tests and for building Python packages.

@@

\paragraph{\emph{F2PY.}}  The program \code{f2py} is a tool for
building NumPy-aware Python wrappers of Fortran functions.
NumPy itself does not use any Fortran code;  F2PY is part of NumPy
for historical reasons.

\subsection*{Governance}

@@

\subsection*{Funding}

@@

\subsection*{Developers}

@@

\subsection*{Community calls}

@@

\subsection*{NumPy enhancement proposals}

@@

\subsection*{Central role}

@@

\subsection*{Wheels build system}

@@

\subsection*{Recent technical improvements}

@@

\subsection*{Array function protocol}

@@

\subsection*{Random number generation}

@@

\subsection*{Testing on multiple architectures}

>>>>

@@

\section*{Library organization}

@@

\subsection*{Core}

The \code{ndarray} data structure and the
universal functions make up the core of NumPy.

@@

\subsection*{Computing libraries.}

NumPy provides a large library of functions for array manipulation
and scientific computing, including functions for: creating, reshaping,
concatenating, and padding arrays; searching, sorting and counting data
in arrays; computing elementary statistics, such as the mean, median,
variance, and standard deviation; file I/O; and more.

@@

\subsection*{Infrastructure libraries}

NumPy provides utilities for writing tests and for building Python packages.

@@

\subsection*{F2PY}  The program \code{f2py} is a tool for
building NumPy-aware Python wrappers of Fortran functions.
NumPy itself does not use any Fortran code;  F2PY is part of NumPy
for historical reasons.

\section*{Governance}

@@

\section*{Funding}

@@

\section*{Developers}

@@

\section*{Community calls}

@@

\section*{NumPy enhancement proposals}

@@

\section*{Central role}

@@

\section*{Wheels build system}

@@

\section*{Recent technical improvements}

@@

\section*{Array function protocol}

@@

\section*{Random number generation}

@@

\section*{Testing on multiple architectures}

### 2020-05-23 supplementary.tex
Move methods to standalone PDF

\title{Array Programming with NumPy}

@@

\keywords{Scientific computing, Python, Mathematics, Array Programming}

@@

\input{body}

@@

\section*{Acknowledgments}

We thank Ross Barnowski, Paul Dubois, Michael Eickenberg, and Perry Greenfield, who
suggested text and provided helpful feedback on the manuscript.

We also thank the many members of the community who provided
feedback, submitted bug reports, made improvements to the documentation,
code, or website, promoted NumPy's use in their scientific fields, and built
the vast ecosystem of tools and libraries around NumPy.
We also gratefully acknowledge the Numeric and Numarray developers
on whose work we built.

Jim Hugunin wrote Numeric in 1995, while a graduate student at MIT.
Hugunin based his package on previous work by Jim Fulton, then working at the
US Geological Survey, with input from many others.
After he graduated, Paul Dubois at the Lawrence Livermore National Laboratory
became the maintainer.
Many people contributed to the project including T.E.O. (a co-author
of this paper), David Ascher, Tim Peters, and Konrad Hinsen.

In 1998 the Space Telescope Science Institute started using Python
and in 2000 began developing a new array package called Numarray, written
almost entirely by Jay Todd Miller, starting from a prototype developed by
Perry Greenfield.  Other contributors included Richard L. White, J. C. Hsu,
Jochen Krupper, and Phil Hodge.
The Numeric/Numarray split divided the community, yet ultimately pushed
progress much further and faster than would otherwise have been possible.

Shortly after Numarray development started, T.E.O. took over maintenance of
Numeric. In 2005, he led the effort and did most of the work to unify Numeric
and Numarray, and produce the first version of NumPy.

Eric Jones co-founded (along with T.E.O. and P.P.) the SciPy community, gave early feedback on array
implementations, and provided funding and travel support to several
community members.
Numerous people contributed to the creation and
growth of the larger SciPy ecosystem, which gives NumPy much of its
value. Others injected new energy and ideas by creating experimental
array packages.

K.J.M. and S.J.v.d.W. were funded in part by the Gordon and Betty Moore
Foundation through Grant GBMF3834 and by the Alfred P. Sloan Foundation through
Grant 2013-10-27 to the University of California, Berkeley.
S.J.v.d.W., S.B., M.P., and W.W. were funded in part by the Gordon
and Betty Moore Foundation through Grant GBMF5447 and by the Alfred
P. Sloan Foundation through Grant G-2017-9960 to the University of
California, Berkeley.

\section*{Author Contributions Statement}

K.J.M. and S.J.v.d.W. composed the manuscript with input from others.
S.B., R.G., K.S., W.W., M.B., and T.J.R. contributed text.
All authors have contributed significant code, documentation, and/or expertise
to the NumPy project.
All authors reviewed the manuscript.

\section*{Competing Interests}

The authors declare no competing interests.

>>>>

\title{Supplementary Methods}

@@

@@

\input{methods}

@@
